Policy optimization for dynamic spatiotemporal systems \hspace{1em} \insertframenumber

### 2014-08-04 pot/LaTeX/jsm2014.tex
maps and troubleshooting
map updates

@@

\begin{frame}{Data analysis}
  \begin{itemize} \setlength{\itemsep}{0.5em}
    \item Ozone analysis at 85 sites in NC, SC, and GA for 92 days
    \includegraphics[width=1\linewidth]{./plots/ozone_station.pdf}
  \end{itemize}
\end{frame}

>>>>

\begin{frame}{Example daily partition}
	Two sample partitions
    \centering
    \includegraphics[width=0.54\linewidth]{./plots/example-partition-1.pdf}
    \includegraphics[width=0.54\linewidth]{./plots/example-partition-2.pdf}
\end{frame}

@@

\begin{frame}{Data analysis}
  \begin{itemize} \setlength{\itemsep}{0.5em}
    \item Max 8-hour ozone measurements at 85 sites in NC, SC, and GA for 92 days
    \includegraphics[width=1\linewidth]{./plots/ozone_station.pdf}
  \end{itemize}
\end{frame}

\begin{frame}{$\chi$-plot for selected ozone sample quantiles}
	\centering
    \includegraphics[width=1\linewidth]{./plots/chi-plot-ozone-res.pdf}
\end{frame}
